Multiresolution Neural Field Estimation

### 2011-03-01 Multiresolution_framework/ltx/manuscript.tex
edit to spatial freq analysis

 \cut{Hence, the algorithm has two distinct steps: the E-step which computes $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step which updates the paramter estimates by computing the (analytic) maximum of $Q(\theta,\theta')$. The EM algorithm iterates between these two steps until the parameter estimates converge.} 

@@

 \cut{The spatial frequency of the observed field is shown in \figurename{\ref{fig:KernelAndFreqResponse}} (b), showing a spatially band-limited signal. This suggests the use of wavelets up to level $j=2$ (with the bandwidth $\approx[2.5,4]$ cycles/mm) can fully represent the field. Note that wavelets due to their bandpass filter characteristics extract successively higher and higher frequency components by increasing $j$.}

>>>>

 \cut{The algorithm has two steps: the E-step which computes $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ based on the most recent parameter estimates using the RTS smoother, and the M-step which updates the parameter estimates by computing the (analytic) maximum of $Q(\theta,\theta')$. The EM algorithm iterates between these two steps until the parameter estimates converge.} 

@@

The spatial cutoff frequency of the observed field was used to specify the level of decomposition required to represent the field using the wavelets. Fig.~\ref{fig:KernelAndFreqResponse} (b), shows the field spatial frequency and cuttoff of \dean{??}. Therefore, wavelets up to level $j=2$ (with the bandwidth $\approx[2.5,4]$ cycles/mm) can represent the significant spatial characteristics of the field. \cut{Note that wavelets due to their bandpass filter characteristics extract successively higher and higher frequency components by increasing $j$.}
